\plaintitle

### 2018-03-31 paper/paper.tex
...

We propose a command translationi system with which we can

@@

\subsection{Title and Authors}

\subsection{Subsequent Pages}

\section{Acknowledgments}

>>>>

We propose a command translation system with which users can get a complete
command string

@@

Contributions of this paper are as follows:

\begin{enumerate}
% 各種技術を組み合わせた翻訳支援というパラダイムの提案
\item Introduction of a ``translation paradigm''
\item IME-like command etnry system
% やりたいことを実行するインタフェース (IME的なもの)
\item Flexible dynamic search system based on RegExp (ExpandHelp)
% そのための柔軟なインフラ (ExpandHelp)
\item Data sharing infrastructure for the translation paradigm
% 共有/編集しやすい正規表現DSLとそのインプリ(Scrapbox+)
% \item これが唯一の解決法ではないが、こういう考え方がポピュラーになって欲しい
\end{enumerate}

\section{Example}

We have implemented ``GitHtlp'' that
